Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-24 paper/pears.tex
switched plots to newest vers and added combo plots for scaled sep and vel

  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{stellarmass_distribution_1000.png}
    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
  \end{figure*}

@@

%% pair fraction plot
\label{sec:results}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{pairratio_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.\todo{remove "difference" label, explain in capt. what "diff" means}}
  \label{fig:pairratio}
\end{figure*}

@@

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
  % Massive Pairs
  The separation between major (minor) massive pairs, on the other hand, increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
  % Difference plots
  (Bottom) The median difference and 1-99\% range of the difference between major and minor pairs from 1000.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution_1000.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
    }
  \label{fig:sep-dist}
\end{figure*}

@@

%% velocity plots 
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{velocity_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:vel}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution_1000.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
  At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
  Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
  The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
    }
  \label{fig:vel-dist}
\end{figure*}
%%%

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_1000.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
    }
  \label{fig:sep-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_distribution_1000.png}
  \caption{\todo{finish caption}}
  \label{fig:sep-scaled-dist}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_1000.png}
  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
  }
  \label{fig:vel-scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_distribution_1000.png}
  \caption{\todo{finish caption}}
  \label{fig:vel-scaled-dist}
\end{figure*}

>>>>

  \begin{figure*}[htp]
    \centering
    \includegraphics[width=\textwidth]{smrdist_1000.png}
    \caption{Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
  \end{figure*}

@@

%% pair fraction plot
\label{sec:results}
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{pairfrac_1000.png}
  \caption{
    % Top plots ~
    (Top) Median fraction of dwarf or massive primaries with a major or minor companion by stellar mass. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
      % massive pairs
    The fraction of massive primaries (pink) with a major (left) or minor (right) companion remains approximately constant for $z>1$, with an average pair fraction of 0.16-0.17 and 0.14-0.15 respectively. Between $z=0.25$ and $z=0$, the massive major pair fraction increases sharply from 0.165 to 0.207, a 25\% increase, while the minor pair fraction increases from 0.127 to 0.152, a 20\% increase.
      % dwarf pairs
    Dwarf pairs (green), on the other hand, have pair fractions that are approximately constant from $z=3-4$, but the fraction of major(minor) pairs declines monotonically from 0.126(0.111) at x=3 to just 0.041(0.034) at x=0, a 67(70)\% decrease. 
    % Bottom plots ~
  (Bottom) The median subtracted difference between the massive pair fraction and the dwarf pair fraction, with the shaded $1$-$99$ percentile range of the difference of each realization. The difference between the massive pair fraction and dwarf pair fraction increases with decreasing redshift, peaking at $z=0$ with a difference of 0.166 for major pairs and 0.111 for minor pairs. This shows that the redshift evolution of the pair fractions of massive pairs and dwarf pairs proceed differently, particularly in the low redshift regime.\todo{remove "difference" label, explain in capt. what "diff" means}}
  \label{fig:pairratio}
\end{figure*}

@@

%% separation plots
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{sep_1000.png}
  \caption{(Top) Median physical separation (in kpc) of dwarf pairs (left, green) and massive pairs (right, pink) as a function of redshift. 
  Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. 
  Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
  In general, as the redshift decreases from $z=4$ to $z=0$, the average physical separation of a pair increases for both dwarf and massive pairs. 
  % Dwarf pairs
  The typical separation between major (minor) dwarf pairs increases from $42(38)\,\kpc$ at $z=4$ to a peak of $128(109)\,\kpc$ at $z=0$.
  % Massive Pairs
  The separation between major (minor) massive pairs, on the other hand, increases from $81(71)\,\kpc$ at $z=4$ to $288(205)\,\kpc$ at  $z=0$.
  % Difference plots
  (Bottom) The median difference and 1-99\% range of the difference between major and minor pairs from 1000.
  Minor dwarf pairs tend to be $\sim10-20\kpc$ closer to their primary than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{sepdist_1000.png}
  \caption{Normalized physical separation distribution for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median separation of each pair type from the previous plot is shown in solid (major) and dotted (minor) vertical black lines. 
  At higher redshift $z=3-4$, a large fraction of both dwarf and massive pairs have low separations ($<$ 125 \& 250 $\kpc$ respectively). However, at low redshift, the separation distribution tends to spread out more evenly across a large range of separations, thus increasing the median.
    }
  \label{fig:sep-dist}
\end{figure*}

@@

%% velocity plots 
\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{vel_1000.png}
  \caption{
    (Top) Median relative velocity (in \kms) between the primary and secondary halos of: dwarf pairs (left, green), and massive pairs (right, pink) as a function of redshift. 
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations. Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines.
    The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs.
    As the redshift decreases from $z=4$ to $z=0$, the average relative velocity of a pair decreases as well for both dwarf and massive pairs.
    % brief describe
    The median relative velocity of a dwarf pair (major or minor) is $70\,\kms$ at $z=0$ and $133\,\kms$ at $z=4$, and of a massive pair is $170\,\kms$ at $z=0$ and $260\,\kms$ at $z=4$ ($295\,\kms$ for a minor pair). 
    % Difference plot
    (Bottom) The median subtracted relative velocity difference between major and minor pairs, and 1-99\% shaded region.
    The is little difference between major and minor dwarf pairs (bottom left), with minor pairs having a relative velocity of $0-5\,\kms$ higher than major pairs. 
    Major and minor massive pairs also have very little median velocity difference at low redshift (bottom right), with minor pairs having a relative velocity between $1-20\,\kms$ faster than major pairs.
    \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:vel}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{veldist_1000.png}
  \caption{
  Normalized distribution of relative velocities between primary and secondary halos for dwarf (top) and massive (bottom) pairs from $z=0$ (left) to $z=4$ (right). Major pairs are shown as solid lines, while minor pairs are dotted. The median relative velocity of each pair type from Fig.~\ref{fig:vel} is shown in solid (major) and dotted (minor) vertical black lines. 
  %
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. 
  At $z=0$, typical dwarf pair relative velocities are $0-200\,\kms$, while at $z=4$ they are $0-300\,\kms$. 
  Massive pairs typically have relative velocities between $0-300\,\kms$ at z=0 and $0-400\,\kms$ at $z=4$.
  The distribution of velocities for major and minor pairs is roughly equivalent within each mass range. 
    }
  \label{fig:vel-dist}
\end{figure*}
%%%

@@

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledcombo_1000.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Ma-Dw" means}
  Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.
  \todo{finish caption} \todo{remove "difference" legend, explain in capt. what "Maj-Min" means}
    }
  \label{fig:scaled}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=\textwidth]{scaledcombodist_1000.png}
  \caption{\todo{finish caption}}
  \label{fig:scaled-dist}
\end{figure*}
